### 2015-01-18 src/conclusion.Rnw
update

Our analysis suggests that while some of the different strategies produce
slightly advantageous mutation subsets, overall, the advantage thus gained
is very little. None of the common operator selection strategies performed
consistently well against random sampling while using either the utility or
the mutation effectiveness criteria. While some of the individual operators
such as \Pitrv, \Piti, \Pitri, and \Pites~show promise in test utility,
they do not stand out when we examine the mutation effectiveness in comparison
to baseline.

A similar result seems to be the case for operator based x\% selection
strategy or even for the element based x\% strategy. They in general show a
slight advantage in test utility which doesn't seem to translate to the
strategy effectiveness in comparison with baseline.

Thus we find that that none of the well known reduction strategies are actually
able to consistenly select useful mutants, and the best path forward
for a working tester is to rely on the simplest scheme of all -- the random
selection of mutants.

>>>>

Our analysis suggests that while some of the different strategies produce
slightly advantageous mutation subsets, overall, the advantage thus gained
is very little. None of the common operator selection strategies performed
consistently well against random sampling while using either the utility or
the mutation effectiveness criteria. While some of the individual operators
seemed to indicate a mean positive test utility or a mean strategy
effectiveness, the effect itself is too small (of the order of one or two
mutants or tests) to be of much help for a tester in the real world.

A similar result seems to be the case for operator based x\% selection
strategy or even for the element based x\% strategy. They in general show a
slight advantage in test utility which while consistent, is not of much
practical utility.

This suggests that that none of the well known reduction strategies are
actually able to consistenly select useful mutants, and the best path forward
for a working tester is to rely on the simplest scheme of all -- the random
selection of mutants.
